Covariant Phase Space via MultiSymplectic Geometry

### 2017-06-13 cpsviams.tex
New picture on the convariant approach.

\section{Jacobi Operator}\label{Sec:JacobiOperator}
Intuitively, the Jacobi equations are the formal linearization of the equation of motion around a solution $\phi$.\\
Everything can be encoded in the following operator:
%
	\begin{definition}[Jacobi operator pertaining to $D$ around a solution $\phi \in \Sol$]\label{Def:JacobiOp} is the bundle map over $F$:
		\begin{displaymath}
			J(\phi) \; : \; \phi^\ast(VF) \rightarrow	\phi^\ast(V^\TwistedLinear F) 
			\quad s.t. \quad  \left(J(\phi)\right) V
			= \sigma \left( \left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda](x) \right\rvert_{\lambda=0} \right)
		\end{displaymath}
		where $V\in (\phi^\ast(VF))_{\phi(x)} = V_{\phi(x)}F$ and $\phi_\lambda$ is a regular variation generated by a $\delta\phi$ such that $\delta\phi_x = V$ and
		$\sigma$ is the canonical bundle-morphism \footnote{see \ref{Section:sigma} for further details.}
		\begin{displaymath}
			\sigma:  0^\ast \left( V_M W \right)  \; \rightarrow \;  0^\ast \left(V_E W \right) \simeq W
		\end{displaymath}
		 where $V_M W$ and $V_F W$ are the vertical sub-bundle of $T W$ w.r.t. $M$ and $F$ respectively 
		 and $0$ is the zero-section of $W$ over $F$.
	\end{definition}
	%
	\begin{remark}
		Being $J$ a bundle morphism, it can be naturally interpreted functionally as
		\begin{displaymath}
			\left(J(\phi)\right) [\: ] : 
			\Gamma^\infty\left(\phi^\ast(VF)\right) \rightarrow	
			\Gamma^\infty \left( 
			\phi^\ast(V^\TwistedLinear F)
			\right)
		\end{displaymath}
	\end{remark}
%
  \begin{minipage}[r]{0.5\textwidth}
    \includegraphics[width=0.85\textwidth]{Pictures/Jacobi.png}
  \end{minipage}\hfill
  \begin{minipage}[l]{0.5\textwidth}
	Note that $ \left(J(\phi)\right) [ \delta\phi ]$ and $D$ mapt to the same space.
  \end{minipage}

Since $D[\phi_\lambda](x)$ is a smooth curve on $ V^\TwistedLinear F $, that is also vertical w.r.t. $M$, 
the derivative involved has to be intended as the tangent velocity vector,
thus $\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]$ is the vertical vector field associated to the infinitesimal variation.\\
Exactly as noted for the tangent vector of $\Conf$, we have for any $x\in M$:
		\begin{displaymath}
			\left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]\right\rvert_{\lambda=0}(x) \in V_M W
			\quad \Rightarrow \quad
			\left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]\right\rvert_{\lambda=0} \in D[\phi]^\ast \left( V_M \left( V^\TwistedLinear \right)\right)
		\end{displaymath}
		because $D[\phi_\lambda]$ can be regarded as a section of $V^\TwistedLinear F$ over $M$.
		Hence the latter definition does not depend from the particular choice of variation $\phi_\lambda$ 
		but only from its infinitesimal generator $\delta\phi$.

>>>>

\section{Jacobi Operator}\label{Sec:JacobiOperator}
Intuitively, the Jacobi equations are the formal linearization of the equation of motion around a solution $\phi$.\\
Everything can be encoded in the following operator:
%
	\begin{definition}[Jacobi operator pertaining to $D$ around a solution $\phi \in \Sol$]\label{Def:JacobiOp} is the bundle map over $F$:
		\begin{displaymath}
			J(\phi) \; : \; \phi^\ast(VF) \rightarrow	\phi^\ast(V^\TwistedLinear F) 
			\quad s.t. \quad  \left(J(\phi)\right) V
			= \sigma \left( \left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda](x) \right\rvert_{\lambda=0} \right)
		\end{displaymath}
		where $V\in (\phi^\ast(VF))_{\phi(x)} = V_{\phi(x)}F$ and $\phi_\lambda$ is a regular variation generated by a $\delta\phi$ such that $\delta\phi_x = V$ and
		$\sigma$ is the canonical bundle-morphism \footnote{see \ref{Section:sigma} for further details.}
		\begin{displaymath}
			\sigma:  0^\ast \left( V_M W \right)  \; \rightarrow \;  0^\ast \left(V_E W \right) \simeq W
		\end{displaymath}
		 where $V_M W$ and $V_F W$ are the vertical sub-bundle of $T W$ w.r.t. $M$ and $F$ respectively 
		 and $0$ is the zero-section of $W$ over $F$.
	\end{definition}
	%
	\begin{remark}
		Being $J$ a bundle morphism, it can be naturally interpreted functionally as
		\begin{displaymath}
			\left(J(\phi)\right) [\: ] : 
			\Gamma^\infty\left(\phi^\ast(VF)\right) \rightarrow	
			\Gamma^\infty \left( 
			\phi^\ast(V^\TwistedLinear F)
			\right)
		\end{displaymath}
	\end{remark}
%
  \begin{minipage}[r]{0.80\textwidth}
  	\includestandalone[width=0.85\textwidth]{Pictures/Figure_Jacobi}
    %\includegraphics[width=0.85\textwidth]{Pictures/Jacobi.png}
  \end{minipage}\hfill
  \begin{minipage}[l]{0.20\textwidth}
	Note that $ \left(J(\phi)\right) [ \; ]$ and $D[\;]$ maps to the same space.
  \end{minipage}

\vspace{5mm}
Since $D[\phi_\lambda](x)$ is a smooth curve on $ V^\TwistedLinear F $, that is also vertical w.r.t. $M$, 
the derivative involved has to be intended as the tangent velocity vector,
thus $\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]$ is the vertical vector field associated to the infinitesimal variation.\\
Exactly as noted for the tangent vector of $\Conf$, we have for any $x\in M$:
		\begin{displaymath}
			\left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]\right\rvert_{\lambda=0}(x) \in V_M W
			\quad \Rightarrow \quad
			\left.\dfrac{\diff}{\diff \lambda} D [\phi_\lambda]\right\rvert_{\lambda=0} \in D[\phi]^\ast \left( V_M \left( V^\TwistedLinear \right)\right)
		\end{displaymath}
		because $D[\phi_\lambda]$ can be regarded as a section of $V^\TwistedLinear F$ over $M$.
		Hence the latter definition does not depend from the particular choice of variation $\phi_\lambda$ 
		but only from its infinitesimal generator $\delta\phi$.
